Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2001-01-01 paper.tex
Add theta distributions for nsns model

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-luminosity_R}
  \caption{Radial number fluxes, $K_r$, as functions of colatitude $\theta$.
    Sampled for observers at fixed coordinate distances from the center
    of the star, with $r=250\,{\rm km}$.
    Here radial fluxes are multiplied by the portion of solid angle
    represented by each observer, so that the total luminosity is
    computed by summing all the points.}
  \label{fig:nsns_theta_distrib_R}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-luminosity_L}
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_R} but radial energy
    fluxes, $H_r$.}
  \label{fig:nsns_theta_distrib_L}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-avg_eps}
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_R} but
    average energies $\langle \varepsilon \rangle = J/G$.}
  \label{fig:nsns_theta_distrib_avg_eps}
\end{figure}
